---
#  GSoC Hard Task: download a HF data set and convert it to a Task. (using only R code, not python nor reticulate)
---
#                              1] My Logic & Dataset Choice

## Iris Dataset Implementation
<U>I started with the Iris dataset because it is the standard for testing HARD TASK. My purpose here was to establish a concept for the simple download of a HF dataset and its direct conversion into an 'mlr3' task.</U>




```text
+-------------------------------------------------------------------------------|
|      IRIS DOWNLOAD PROCEDURE                                                  |
+-------------------------------------------------------------------------------|
|                                                                               |
|  1]SITE WHICH IS MENTIONED ON WIKI !                                          |
|   (https://huggingface.co/datasets)                                           |
|               |                                                               |
|               v                                                               |
|  2]     IRIS DATASET                                                          |
|     (Repo: scikit-learn/iris)                                                 |
|               |                                                               |             
|               v                                                               |
|  3] GONE INTO 'FILES AND VERSIONS'                                            |
|         ( 'Iris.csv')                                                         |
|               |                                                               |
|               v                                                               |
|  4]  COPY DOWNLOAD  LINK                                                      |
|   (https://huggingface.co/datasets/scikit-learn/iris/resolve/main/Iris.csv)   | 
|                                                                               | 
|                                                                               |
+-------------------------------------------------------------------------------|
```

#                                 2]CODE OF IRIS (BASIC)
```{r}
   
library(mlr3)

                        # 1] Download-
 iris_url <- "https://huggingface.co/datasets/scikit-learn/iris/resolve/main/Iris.csv"
 iris_df  <- read.csv(iris_url, stringsAsFactors = TRUE)
 
 iris_df$Id <- NULL      
 
                       # 2] Initialize Task 
 task_iris <- as_task_classif(iris_df, target = "Species", id = "iris")
 
 # 3] Calling the Task
 print(task_iris)
```

#                                 3] ANOTHER DATASET (Continued)

## Pima Indians Diabetes Implementation
<U>When  I successfully understood the dataset of Iris, I implemented the Pima Indians Diabetes dataset to **strengthen the hard task**. Moving to this dataset allowed me to demonstrate more  data handling, such as managing binary classes and ensuring correct feature types in a real-world medical context.</U>

---



```text
+---------------------------------------------------------------------------------------------------------|
|      PIMA DOWNLOAD PROCEDURE                                                                            |
+---------------------------------------------------------------------------------------------------------|
|                                                                                                         |
|  1]SITE WHICH IS MENTIONED ON WIKI !                                                                    |
|    (https://huggingface.co/datasets)                                                                    |
|               |                                                                                         |
|               v                                                                                         |
|  2] PIMA INDIANS DIABETES DATASET                                                                       |
|                                                                                                         |  
|     ( khoaguin/pima-indians-                                                                            |
|         diabetes-database)                                                                              |
|               |                                                                                         |
|               v                                                                                         |
|  3] GONE INTO 'FILES AND VERSIONS'                                                                      |
|        ('diabetes.csv')                                                                                 |
|               |                                                                                         |
|               v                                                                                         | 
|  4] COPY DOWNLOAD LINK                                                                                  |
|     (https://huggingface.co/datasets/khoaguin/pima-indians-diabetes-database/resolve/main/diabetes.csv) |
|                                                                                                         |
|                                                                                                         |
+---------------------------------------------------------------------------------------------------------|
```
#   NOTE:- FLOwCHART ARE MENSIONED TO IDENTIFY HUGGING FACE DATASET DOWNLOAD PROCEDURE.

#                     4] CODE OF PIMA INDIAN DIABETES

```{r}
  
library(mlr3)

                                 # 1] Download
 pima_url <- "https://huggingface.co/datasets/khoaguin/pima-indians-diabetes-database/resolve/main/diabetes.csv"
 pima_df  <- read.csv(pima_url)


 pima_df$y <- as.factor(pima_df$y)

                            # 2] Initialize Task 
 task_pima <- as_task_classif(pima_df, target = "y", id = "pima")

 # 3]  Calling the Task
 print(task_pima)
```